---
title: "Summary of exploratory tasks"
author: 'Daniel Yan, Christina Cui, Sophie Shi, Henry Louie'
date: today
code-fold: true
---

```{r output = FALSE}
library(tidyverse)
library(kableExtra)
```

### HTML scraping

Does including header content improve predictions? Answer the question and provide quantitative evidence supporting your answer.

The inclusion of header content did not significantly change the predictions. Below we can see the error metrics for the base logistic regression model run on just the text data. 

```{r}
#load base logistic regression metrics
load("../results/base-logreg-model/base_metrics.RData")

#load header logistic regression metrics
load("../results/headings_metrics.RData")

base_metrics %>% 
  kable() %>% 
  kable_styling(full_width = FALSE)
```

We can see that our area under the ROC curve is approximately 0.8666 and the accuracy of the model was approximately 0.7973 on a testing split. Now comparing that to the metrics of the logistic regression model run with heading data included: 

```{r}
headings_metrics %>% 
  kable() %>% 
  kable_styling(full_width = FALSE)
```

We can see that the area under the ROC curve dropped down to 0.8486 while the accuracy of the model rose slightly to 0.7987 on a testing split. This indicates that the models are quite similar in performance to each other and as such it does not seem that including header data improved predictions. 

### Bigrams

Do bigrams capture additional information relevant to the classification of interest? Answer the question, **briefly** describe what analysis you conducted to arrive at your answer, and provide quantitative evidence supporting your answer.

### Neural net

Summarize the neural network model you trained by desribing:

-   architecture

-   optimization and loss

-   training epochs

-   predictive accuracy
